*Computational thinking 1*

The reading exercises can be found [here](reading.md).

The assessment is below.

*Team Ctenophora*

Q1

```{r}

species_codes <- c( "GREG" = "Great Egret", "MALL" = "Mallard", "MAWR" = "Marsh Wren", "KILL" = "Killdeer"
)

sightings = c("GREG", "GREG", "MALL", "MAWR", "KILL", "GREG")

# Modify this line to use species_codes so your counts have common names

sightings <- table(sightings)
sightings[]

names(sightings) <- species_codes

```

Q2

Why adding 1 to a POSIXct datetime object increments it by a second - because the value of POSIXct vectors represents the number of seconds since January 1, 1970 (a double) and spit out a datetime format.

The default origin is 1970-01-01.

```{r}
new_now <- as.POSIXct(0, origin = "2000-01-01 12:00:00", tz = "UTC")
```

How to take away the POSIXct class?

```{r}
new_now
```

Q3

```{r}
x <- list(1, 2, 3)
y <- x[2]
z <- x[[2]]

class(y)
class(z)
```

Y is a list, while z is numeric. It's because of the double brackets, which means that you can subset the section without getting the "title".

Q4

In data frames, the elements of the list are the columns, and length() is equivalent to nrows(). I don't know why!!

Q5

```{r}
experiment <- data.frame(
    plot = c("p1", "p2", "p3", "p4"),
    N_g = c(0.2, 0.7, 0.3, 0.2),
    P_g = c(0.1, 0.1, 0.5, 0.6)
)

nutrient <- "N_g"
```

I would use experiment\$N_g. It would not change, because it is already numeric, and atomic vectors include logicals, integers, complex, etc.

Q6

```{r}
library(palmerpenguins) 
penguins_by_island <- split(penguins, penguins$island)
mean_mass <- list(
    Biscoe = mean(penguins_by_island$Biscoe$body_mass_g, na.rm = TRUE),
    Dream = mean(penguins_by_island$Dream$body_mass_g, na.rm = TRUE),
    Torgersen = mean(penguins_by_island$Torgersen$body_mass_g, na.rm = TRUE)
)
```

The function split() divides the data (first argument) and reassembles it into groups defined by the second argument.

In mean_mass, we create a list containing each Island and the mean mass of penguins on that island. We remove NAs. We subset each island by taking our grouped data frame, subsetting by the island, and then selecting the body mass column.
